Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-28 ms.qmd
Response about figures, and predcition intervals

We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers. `r utils::packageVersion("metafor")` @Viechtbauer2010-fn]. We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers. 2.0, @Nakagawa2021-ls; @nakagawaorchard]. In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz]. In all cases, frequentist and Bayesian models resulted in the same conclusions. For our Bayesian models, we ran 4 MCMC chains, each with a warm-up (burn-in) of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution. We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}$(3, 0, 10)). We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat}$ = 1). 
We also explored the potential for publication bias in our dataset but there was no evidence it existed (details in *Supplementary Materials*).

>>>>

We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers.
`r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2017-wg; @Burkner2018-ur; @noauthor_2021-az] and *metafor* [vers. `r utils::packageVersion("metafor")` @Viechtbauer2010-fn]. We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots that more easily convey heterogeneity in effects with prediction intervals [vers. 2.0, @Nakagawa2021-ls; @nakagawaorchard]. Prediction intervals can be interpreted as the range of expected effects from future studies [@Noble2022-ty]. In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021-uf; @Song2021-ba; @Noble2017-mz]. In all cases, frequentist and Bayesian models resulted in the same conclusions. For our Bayesian models, we ran 4 MCMC chains, each with a warm-up (burn-in) of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a minimum of 3200 samples from the posterior distribution. We used flat Gaussian priors for 'fixed' effects (i.e.,$N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}$(3, 0, 10)). We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat}$ = 1). 
We also explored the potential for publication bias in our dataset but there was no evidence it existed (details in *Supplementary Materials*).
